Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-24 ms.tex
more work on intro

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}
\newcommand{\COBE}{{\it COBE}}

@@

%basic background about interstellar dust emission
Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m with inferior 0.7$^{\circ}$ angular resolution, but 
with a reliable zero point \citep{boggess92}. \COBE/FIRAS \citep{firas} also 
provided full-sky infrared dust spectra at $7^{\circ}$ resolution in 213 narrow
frequency bins between 30 GHz and 2850 GHz.

\citet[hereafter FDS99]{FDS99} used FIRAS data to derive a globally best-fit 
model of dust emission applicable over a very broad range of frequencies. 
FDS99 showed that no model consisting of a single modified blackbody (MBB) 
could accurately match the \IRAS/FIRAS/DIRBE spectrum at both the Wien and 
Rayleigh-Jeans extremes. To fit both ends of the spectrum, FDS99 therefore 
proposed a dust emission model consisting of two MBBs, each with a different 
temperature and power law index. Physically, these two components might 
represent distinct dust grain species within the ISM, namely amorphous 
silicates and carbonaceous grains.

@@

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative parametrization for the dust spectral energy distribution 
(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ 
resolution maps of dust temperature and optical depth. Because we employ a 
model that has been validated with FIRAS data down to sub-mm wavelengths, we 
expect our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a useful comparison for extinction 
estimates based directly upon optical/NIR observations of stars. % and as
% a baseline or a next generation dust extinction map incorporating
% high resolution, fulls-sky infrared data sets such as WISE and Akari.

>>>>

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\PLANCK}{{\it Planck}}
\newcommand{\AKARI}{{\it Akari}}
\newcommand{\COBE}{{\it COBE}}
\newcommand{\WISE}{{\it WISE}}

@@

Over the past decades, satellite observations have dramatically enhanced our
knowledge about infrared emission from the ISM. The \textit{Infrared Astronomy 
Satellite} (\IRAS), with its $\sim$4$'$ resolution, revolutionized the study of
 Galactic dust emission, first revealing the high-latitude ``infrared cirrus'' 
using 60$\mu$m and 100$\mu$m observations \citep{low84, wheelock94}. Later, the
Diffuse Infrared Background Experiment (DIRBE) aboard the \COBE~satellite 
provided complementary full-sky measurements at ten infrared wavelengths from 
1.25$\mu$m to 240$\mu$m, boasting a reliable zero point despite inferior 
$\sim$0.7$^{\circ}$ angular resolution \citep{boggess92}. \COBE/FIRAS 
\citep{firas} also provided full-sky infrared dust spectra at $7^{\circ}$ 
resolution in 213 narrow frequency bins between 30 GHz and 2850 GHz.

% DIRBE beam solid angles:
% http://lambda.gsfc.nasa.gov/product/cobe/dirbe_products.cfm

\citet[hereafter FDS99]{FDS99} used these FIRAS data to derive a globally 
best-fit model of dust emission applicable over a very broad range of 
frequencies. FDS99 showed that no model consisting of a single modified 
blackbody (MBB) could accurately match the FIRAS/DIRBE spectrum at both the 
Wien and Rayleigh-Jeans extremes. To fit the thermal dust spectrum between 100 
and 3000 GHz, FDS99 therefore proposed an emission model consisting of two 
MBBs, each with a different temperature and emissivity power law index. 
Physically, these two components might represent distinct dust grain species 
within the ISM, namely amorphous silicates and carbonaceous grains.

% ^^final sentence about what FDS99 meant for foreground predictions (and how
% those predictions actually worked)

%did FDS99 actually use DIRBE (pretty sure they did)

@@

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and \IRAS~100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative parametrization for the dust spectral energy distribution 
(SED) composed  of \PLANCK~and \IRAS~data. In doing so, we obtain $6.1'$ 
resolution maps of dust temperature and optical depth. Because we employ a 
model that has been validated with FIRAS data down to sub-mm wavelengths, we 
expect our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a useful cross-check for extinction 
estimates based directly upon optical observations of stars
\citep[e.g.][]{green14} and as a baseline for next-generation dust extinction 
maps incorporating high-resolution, full-sky infrared data sets such as 
\WISE~\citep{wright10, meisner14} and \AKARI.
